Comparing \pkg{binsegRcpp} with other implementations of binary segmentation for change-point detection

### 2025-05-06 figure-heap-refs-binsegRcpp.tex
direct label in tikz

% Created by tikzDevice version 0.12.6 on 2025-05-06 20:55:50
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (433.62,216.81);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,216.81);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( -0.00,  0.00) rectangle (433.62,216.81);
\end{scope}
\begin{scope}
\path[clip] ( 46.86,116.18) rectangle (226.46,185.23);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 46.86,116.18) rectangle (226.46,185.23);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86,124.04) --
	(226.46,124.04);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86,141.98) --
	(226.46,141.98);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86,159.91) --
	(226.46,159.91);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86,177.84) --
	(226.46,177.84);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86,133.01) --
	(226.46,133.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86,150.94) --
	(226.46,150.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86,168.88) --
	(226.46,168.88);

@@

\path[draw=drawColor,line width= 2.3pt,line join=round] ( 55.03,147.52) --
	( 65.91,140.30) --
	( 76.80,140.31) --
	( 87.68,140.47) --
	( 98.56,141.29) --
	(109.45,142.56) --
	(120.33,143.85) --
	(131.22,145.59) --
	(142.10,147.70) --
	(152.99,150.07) --
	(163.87,152.59) --
	(174.76,155.20) --
	(185.64,157.85) --
	(196.52,160.53) --
	(207.41,163.21) --
	(218.29,165.91);
\definecolor{drawColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 1.1pt,line join=round] (142.10,128.12) --
	(152.99,133.52) --
	(163.87,138.92) --
	(174.76,144.31) --
	(185.64,149.71) --
	(196.52,155.11) --
	(207.41,160.51) --
	(218.29,165.91);

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 65.91,128.12) --
	( 76.80,130.82) --
	( 87.68,133.52) --
	( 98.56,136.22) --
	(109.45,138.92) --
	(120.33,141.62) --
	(131.22,144.31) --
	(142.10,147.01) --
	(152.99,149.71) --
	(163.87,152.41) --
	(174.76,155.11) --
	(185.64,157.81) --
	(196.52,160.51) --
	(207.41,163.21) --
	(218.29,165.91);
\end{scope}
\begin{scope}
\path[clip] ( 46.86,116.18) rectangle (226.46,185.23);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.87,125.28) --
	(142.10,128.12) --
	(150.33,125.28) --
	(150.33,116.41) --
	(133.87,116.41) --
	cycle;

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 59.93,125.28) --
	( 65.91,128.12) --
	( 71.90,125.28) --
	( 71.90,116.41) --
	( 59.93,116.41) --
	cycle;

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (142.10,118.39) {$N^2$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 65.91,118.39) {$N$};
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.86,116.18) rectangle (226.46,185.23);
\end{scope}
\begin{scope}
\path[clip] ( 46.86, 41.62) rectangle (226.46,110.68);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 46.86, 41.62) rectangle (226.46,110.68);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86, 42.48) --
	(226.46, 42.48);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86, 55.84) --
	(226.46, 55.84);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86, 69.20) --
	(226.46, 69.20);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86, 82.55) --
	(226.46, 82.55);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86, 95.91) --
	(226.46, 95.91);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86,109.27) --
	(226.46,109.27);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86, 49.16) --
	(226.46, 49.16);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86, 62.52) --
	(226.46, 62.52);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86, 75.88) --
	(226.46, 75.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86, 89.23) --
	(226.46, 89.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86,102.59) --
	(226.46,102.59);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (214.04, 41.62) --
	(214.04,110.68);
\definecolor{drawColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86, 98.57) -- (226.46, 98.57);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor,fill opacity=0.50] ( 55.03, 53.39) --
	( 65.91, 53.70) --
	( 76.80, 53.42) --
	( 87.68, 53.62) --
	( 98.56, 53.81) --
	(109.45, 52.36) --
	(120.33, 60.85) --
	(131.22, 50.50) --
	(142.10, 53.19) --
	(152.99, 58.46) --
	(163.87, 65.47) --
	(174.76, 72.35) --
	(185.64, 79.70) --
	(196.52, 88.57) --
	(207.41, 97.32) --
	(218.29,107.54) --
	(218.29,106.40) --
	(207.41, 97.20) --
	(196.52, 88.37) --
	(185.64, 79.22) --
	(174.76, 72.10) --
	(163.87, 65.19) --
	(152.99, 58.08) --
	(142.10, 51.77) --
	(131.22, 48.59) --
	(120.33, 47.68) --
	(109.45, 48.68) --
	( 98.56, 51.61) --
	( 87.68, 51.71) --
	( 76.80, 51.86) --
	( 65.91, 51.48) --
	( 55.03, 51.51) --
	cycle;

\path[] ( 55.03, 53.39) --
	( 65.91, 53.70) --
	( 76.80, 53.42) --
	( 87.68, 53.62) --
	( 98.56, 53.81) --
	(109.45, 52.36) --
	(120.33, 60.85) --
	(131.22, 50.50) --
	(142.10, 53.19) --
	(152.99, 58.46) --
	(163.87, 65.47) --
	(174.76, 72.35) --
	(185.64, 79.70) --
	(196.52, 88.57) --
	(207.41, 97.32) --
	(218.29,107.54);

\path[] (218.29,106.40) --
	(207.41, 97.20) --
	(196.52, 88.37) --
	(185.64, 79.22) --
	(174.76, 72.10) --
	(163.87, 65.19) --
	(152.99, 58.08) --
	(142.10, 51.77) --
	(131.22, 48.59) --
	(120.33, 47.68) --
	(109.45, 48.68) --
	( 98.56, 51.61) --
	( 87.68, 51.71) --
	( 76.80, 51.86) --
	( 65.91, 51.48) --
	( 55.03, 51.51);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 2.3pt,line join=round] ( 55.03, 51.80) --
	( 65.91, 51.96) --
	( 76.80, 52.23) --
	( 87.68, 51.97) --
	( 98.56, 51.99) --
	(109.45, 49.61) --
	(120.33, 48.49) --
	(131.22, 49.12) --
	(142.10, 52.46) --
	(152.99, 58.30) --
	(163.87, 65.29) --
	(174.76, 72.20) --
	(185.64, 79.51) --
	(196.52, 88.44) --
	(207.41, 97.24) --
	(218.29,106.51);
\definecolor{drawColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 87.68, 51.15) --
	( 98.56, 56.23) --
	(109.45, 61.15) --
	(120.33, 65.94) --
	(131.22, 70.65) --
	(142.10, 75.28) --
	(152.99, 79.85) --
	(163.87, 84.38) --
	(174.76, 88.87) --
	(185.64, 93.32) --
	(196.52, 97.74) --
	(207.41,102.13) --
	(218.29,106.51);

\path[draw=drawColor,line width= 1.1pt,line join=round] (120.33, 52.22) --
	(131.22, 58.25) --
	(142.10, 64.28) --
	(152.99, 70.31) --
	(163.87, 76.35) --
	(174.76, 82.38) --
	(185.64, 88.41) --
	(196.52, 94.44) --
	(207.41,100.48) --
	(218.29,106.51);

\path[draw=drawColor,line width= 1.1pt,line join=round] (152.99, 58.25) --
	(163.87, 66.29) --
	(174.76, 74.34) --
	(185.64, 82.38) --
	(196.52, 90.42) --
	(207.41, 98.46) --
	(218.29,106.51);

\path[draw=drawColor,line width= 1.1pt,line join=round] (174.76, 58.25) --
	(185.64, 70.31) --
	(196.52, 82.38) --
	(207.41, 94.44) --
	(218.29,106.51);
\end{scope}
\begin{scope}
\path[clip] ( 46.86, 41.62) rectangle (226.46,110.68);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 73.97, 48.31) --
	( 87.68, 51.15) --
	(101.39, 48.31) --
	(101.39, 40.20) --
	( 73.97, 40.20) --
	cycle;

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (111.80, 48.31) --
	(120.33, 52.22) --
	(128.87, 48.31) --
	(128.87, 40.20) --
	(111.80, 40.20) --
	cycle;

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.45, 48.31) --
	(152.99, 58.25) --
	(160.52, 48.31) --
	(160.52, 40.20) --
	(145.45, 40.20) --
	cycle;

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.22, 48.31) --
	(174.76, 58.25) --
	(182.29, 48.31) --
	(182.29, 40.20) --
	(167.22, 40.20) --
	cycle;

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.71] at ( 87.68, 43.40) {$N \log N$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.71] at (120.33, 43.40) {$N^{1.5}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (152.99, 42.12) {$N^2$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (174.76, 42.12) {$N^3$};
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.86, 41.62) rectangle (226.46,110.68);
\end{scope}
\begin{scope}
\path[clip] (231.96,116.18) rectangle (411.55,185.23);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (231.96,116.18) rectangle (411.55,185.23);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (231.96,124.04) --
	(411.55,124.04);

\path[draw=drawColor,line width= 0.3pt,line join=round] (231.96,141.98) --
	(411.55,141.98);

\path[draw=drawColor,line width= 0.3pt,line join=round] (231.96,159.91) --
	(411.55,159.91);

\path[draw=drawColor,line width= 0.3pt,line join=round] (231.96,177.84) --
	(411.55,177.84);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.96,133.01) --
	(411.55,133.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.96,150.94) --
	(411.55,150.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.96,168.88) --
	(411.55,168.88);

@@

\path[draw=drawColor,line width= 2.3pt,line join=round] (240.12,140.30) --
	(247.89,140.30) --
	(255.67,140.31) --
	(263.44,140.47) --
	(271.22,141.29) --
	(278.99,142.56) --
	(286.77,143.85) --
	(294.54,145.59) --
	(302.32,147.70) --
	(310.09,150.07) --
	(317.87,152.59) --
	(325.64,155.20) --
	(333.41,157.85) --
	(341.19,160.53) --
	(348.96,163.22) --
	(356.74,165.91) --
	(364.51,168.60) --
	(372.29,171.30) --
	(380.06,174.00) --
	(387.84,176.70) --
	(395.61,179.40) --
	(403.39,182.10);
\definecolor{drawColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 1.1pt,line join=round] (325.64,128.11) --
	(333.41,133.51) --
	(341.19,138.91) --
	(348.96,144.31) --
	(356.74,149.71) --
	(364.51,155.11) --
	(372.29,160.50) --
	(380.06,165.90) --
	(387.84,171.30) --
	(395.61,176.70) --
	(403.39,182.10);

\path[draw=drawColor,line width= 1.1pt,line join=round] (247.89,128.11) --
	(255.67,130.81) --
	(263.44,133.51) --
	(271.22,136.21) --
	(278.99,138.91) --
	(286.77,141.61) --
	(294.54,144.31) --
	(302.32,147.01) --
	(310.09,149.71) --
	(317.87,152.41) --
	(325.64,155.11) --
	(333.41,157.80) --
	(341.19,160.50) --
	(348.96,163.20) --
	(356.74,165.90) --
	(364.51,168.60) --
	(372.29,171.30) --
	(380.06,174.00) --
	(387.84,176.70) --
	(395.61,179.40) --
	(403.39,182.10);
\end{scope}
\begin{scope}
\path[clip] (231.96,116.18) rectangle (411.55,185.23);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (317.41,125.27) --
	(325.64,128.11) --
	(333.87,125.27) --
	(333.87,116.40) --
	(317.41,116.40) --
	cycle;

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (241.91,125.27) --
	(247.89,128.11) --
	(253.88,125.27) --
	(253.88,116.40) --
	(241.91,116.40) --
	cycle;

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (325.64,118.38) {$N^2$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (247.89,118.38) {$N$};
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (231.96,116.18) rectangle (411.55,185.23);
\end{scope}
\begin{scope}
\path[clip] (231.96, 41.62) rectangle (411.55,110.68);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (231.96, 41.62) rectangle (411.55,110.68);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (231.96, 42.48) --
	(411.55, 42.48);

\path[draw=drawColor,line width= 0.3pt,line join=round] (231.96, 55.84) --
	(411.55, 55.84);

\path[draw=drawColor,line width= 0.3pt,line join=round] (231.96, 69.20) --
	(411.55, 69.20);

\path[draw=drawColor,line width= 0.3pt,line join=round] (231.96, 82.55) --
	(411.55, 82.55);

\path[draw=drawColor,line width= 0.3pt,line join=round] (231.96, 95.91) --
	(411.55, 95.91);

\path[draw=drawColor,line width= 0.3pt,line join=round] (231.96,109.27) --
	(411.55,109.27);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.96, 49.16) --
	(411.55, 49.16);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.96, 62.52) --
	(411.55, 62.52);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.96, 75.88) --
	(411.55, 75.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.96, 89.23) --
	(411.55, 89.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.96,102.59) --
	(411.55,102.59);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (405.36, 41.62) --
	(405.36,110.68);
\definecolor{drawColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.96, 98.57) -- (411.55, 98.57);
\definecolor{fillColor}{RGB}{0,0,0}

>>>>

% Created by tikzDevice version 0.12.6 on 2025-05-06 22:53:29
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (433.62,216.81);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,216.81);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( -0.00,  0.00) rectangle (433.62,216.81);
\end{scope}
\begin{scope}
\path[clip] ( 46.86,116.18) rectangle (226.46,185.23);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] ( 46.86,116.18) rectangle (226.46,185.23);
\definecolor{drawColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86,121.16) --
	(226.46,121.16);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86,137.47) --
	(226.46,137.47);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86,153.77) --
	(226.46,153.77);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86,170.08) --
	(226.46,170.08);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86,129.31) --
	(226.46,129.31);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86,145.62) --
	(226.46,145.62);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86,161.92) --
	(226.46,161.92);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86,178.23) --
	(226.46,178.23);

@@

\path[draw=drawColor,line width= 2.3pt,line join=round] ( 55.03,150.65) --
	( 65.91,144.09) --
	( 76.80,144.10) --
	( 87.68,144.24) --
	( 98.56,144.99) --
	(109.45,146.15) --
	(120.33,147.32) --
	(131.22,148.90) --
	(142.10,150.82) --
	(152.99,152.98) --
	(163.87,155.27) --
	(174.76,157.64) --
	(185.64,160.05) --
	(196.52,162.48) --
	(207.41,164.93) --
	(218.29,167.38);
\definecolor{drawColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 1.1pt,line join=round] (142.10,133.02) --
	(152.99,137.93) --
	(163.87,142.84) --
	(174.76,147.74) --
	(185.64,152.65) --
	(196.52,157.56) --
	(207.41,162.47) --
	(218.29,167.38);

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 65.91,133.02) --
	( 76.80,135.47) --
	( 87.68,137.93) --
	( 98.56,140.38) --
	(109.45,142.84) --
	(120.33,145.29) --
	(131.22,147.74) --
	(142.10,150.20) --
	(152.99,152.65) --
	(163.87,155.11) --
	(174.76,157.56) --
	(185.64,160.01) --
	(196.52,162.47) --
	(207.41,164.92) --
	(218.29,167.38);
\end{scope}
\begin{scope}
\path[clip] ( 46.86,116.18) rectangle (226.46,185.23);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.87,130.17) --
	(142.10,133.02) --
	(150.33,130.17) --
	(150.33,121.31) --
	(133.87,121.31) --
	cycle;

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 59.93,130.17) --
	( 65.91,133.02) --
	( 71.90,130.17) --
	( 71.90,121.31) --
	( 59.93,121.31) --
	cycle;

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (142.10,121.86) {$N^2$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 65.91,121.86) {$N$};
\end{scope}
\begin{scope}
\path[clip] ( 46.86, 41.62) rectangle (226.46,110.68);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] ( 46.86, 41.62) rectangle (226.46,110.68);
\definecolor{drawColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86, 45.09) --
	(226.46, 45.09);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86, 68.35) --
	(226.46, 68.35);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86, 91.60) --
	(226.46, 91.60);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86, 56.72) --
	(226.46, 56.72);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86, 79.97) --
	(226.46, 79.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86,103.23) --
	(226.46,103.23);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (214.04, 41.62) --
	(214.04,110.68);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor,fill opacity=0.50] ( 55.03, 60.40) --
	( 65.91, 60.67) --
	( 76.80, 60.43) --
	( 87.68, 60.60) --
	( 98.56, 60.76) --
	(109.45, 59.50) --
	(120.33, 66.90) --
	(131.22, 57.88) --
	(142.10, 60.23) --
	(152.99, 64.81) --
	(163.87, 70.91) --
	(174.76, 76.91) --
	(185.64, 83.30) --
	(196.52, 91.03) --
	(207.41, 98.65) --
	(218.29,107.54) --
	(218.29,106.55) --
	(207.41, 98.54) --
	(196.52, 90.85) --
	(185.64, 82.89) --
	(174.76, 76.69) --
	(163.87, 70.67) --
	(152.99, 64.48) --
	(142.10, 58.99) --
	(131.22, 56.22) --
	(120.33, 55.43) --
	(109.45, 56.30) --
	( 98.56, 58.85) --
	( 87.68, 58.94) --
	( 76.80, 59.07) --
	( 65.91, 58.74) --
	( 55.03, 58.77) --
	cycle;

\path[] ( 55.03, 60.40) --
	( 65.91, 60.67) --
	( 76.80, 60.43) --
	( 87.68, 60.60) --
	( 98.56, 60.76) --
	(109.45, 59.50) --
	(120.33, 66.90) --
	(131.22, 57.88) --
	(142.10, 60.23) --
	(152.99, 64.81) --
	(163.87, 70.91) --
	(174.76, 76.91) --
	(185.64, 83.30) --
	(196.52, 91.03) --
	(207.41, 98.65) --
	(218.29,107.54);

\path[] (218.29,106.55) --
	(207.41, 98.54) --
	(196.52, 90.85) --
	(185.64, 82.89) --
	(174.76, 76.69) --
	(163.87, 70.67) --
	(152.99, 64.48) --
	(142.10, 58.99) --
	(131.22, 56.22) --
	(120.33, 55.43) --
	(109.45, 56.30) --
	( 98.56, 58.85) --
	( 87.68, 58.94) --
	( 76.80, 59.07) --
	( 65.91, 58.74) --
	( 55.03, 58.77);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 2.3pt,line join=round] ( 55.03, 59.02) --
	( 65.91, 59.16) --
	( 76.80, 59.39) --
	( 87.68, 59.17) --
	( 98.56, 59.18) --
	(109.45, 57.11) --
	(120.33, 56.13) --
	(131.22, 56.68) --
	(142.10, 59.59) --
	(152.99, 64.67) --
	(163.87, 70.76) --
	(174.76, 76.78) --
	(185.64, 83.14) --
	(196.52, 90.91) --
	(207.41, 98.58) --
	(218.29,106.64);
\definecolor{drawColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 87.68, 58.45) --
	( 98.56, 62.87) --
	(109.45, 67.15) --
	(120.33, 71.33) --
	(131.22, 75.42) --
	(142.10, 79.46) --
	(152.99, 83.44) --
	(163.87, 87.38) --
	(174.76, 91.28) --
	(185.64, 95.16) --
	(196.52, 99.01) --
	(207.41,102.83) --
	(218.29,106.64);

\path[draw=drawColor,line width= 1.1pt,line join=round] (152.99, 64.63) --
	(163.87, 71.63) --
	(174.76, 78.64) --
	(185.64, 85.64) --
	(196.52, 92.64) --
	(207.41, 99.64) --
	(218.29,106.64);
\end{scope}
\begin{scope}
\path[clip] ( 46.86, 41.62) rectangle (226.46,110.68);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 69.01, 55.61) --
	( 87.68, 58.45) --
	(106.35, 55.61) --
	(106.35, 44.80) --
	( 69.01, 44.80) --
	cycle;

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (144.76, 55.61) --
	(152.99, 64.63) --
	(161.21, 55.61) --
	(161.21, 46.74) --
	(144.76, 46.74) --
	cycle;

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 87.68, 47.30) {$N \log N$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (152.99, 47.30) {$N^2$};
\end{scope}
\begin{scope}
\path[clip] (231.96,116.18) rectangle (411.55,185.23);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] (231.96,116.18) rectangle (411.55,185.23);
\definecolor{drawColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round] (231.96,121.16) --
	(411.55,121.16);

\path[draw=drawColor,line width= 0.3pt,line join=round] (231.96,137.47) --
	(411.55,137.47);

\path[draw=drawColor,line width= 0.3pt,line join=round] (231.96,153.77) --
	(411.55,153.77);

\path[draw=drawColor,line width= 0.3pt,line join=round] (231.96,170.08) --
	(411.55,170.08);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.96,129.31) --
	(411.55,129.31);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.96,145.62) --
	(411.55,145.62);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.96,161.92) --
	(411.55,161.92);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.96,178.23) --
	(411.55,178.23);

@@

\path[draw=drawColor,line width= 2.3pt,line join=round] (240.12,144.09) --
	(247.89,144.09) --
	(255.67,144.10) --
	(263.44,144.24) --
	(271.22,144.99) --
	(278.99,146.15) --
	(286.77,147.32) --
	(294.54,148.90) --
	(302.32,150.82) --
	(310.09,152.98) --
	(317.87,155.27) --
	(325.64,157.64) --
	(333.41,160.05) --
	(341.19,162.48) --
	(348.96,164.93) --
	(356.74,167.38) --
	(364.51,169.83) --
	(372.29,172.28) --
	(380.06,174.73) --
	(387.84,177.19) --
	(395.61,179.64) --
	(403.39,182.10);
\definecolor{drawColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 1.1pt,line join=round] (325.64,133.01) --
	(333.41,137.92) --
	(341.19,142.83) --
	(348.96,147.74) --
	(356.74,152.65) --
	(364.51,157.55) --
	(372.29,162.46) --
	(380.06,167.37) --
	(387.84,172.28) --
	(395.61,177.19) --
	(403.39,182.10);

\path[draw=drawColor,line width= 1.1pt,line join=round] (247.89,133.01) --
	(255.67,135.47) --
	(263.44,137.92) --
	(271.22,140.38) --
	(278.99,142.83) --
	(286.77,145.28) --
	(294.54,147.74) --
	(302.32,150.19) --
	(310.09,152.65) --
	(317.87,155.10) --
	(325.64,157.55) --
	(333.41,160.01) --
	(341.19,162.46) --
	(348.96,164.92) --
	(356.74,167.37) --
	(364.51,169.83) --
	(372.29,172.28) --
	(380.06,174.73) --
	(387.84,177.19) --
	(395.61,179.64) --
	(403.39,182.10);
\end{scope}
\begin{scope}
\path[clip] (231.96,116.18) rectangle (411.55,185.23);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (317.41,130.17) --
	(325.64,133.01) --
	(333.87,130.17) --
	(333.87,121.30) --
	(317.41,121.30) --
	cycle;

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (241.91,130.17) --
	(247.89,133.01) --
	(253.88,130.17) --
	(253.88,121.30) --
	(241.91,121.30) --
	cycle;

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (325.64,121.86) {$N^2$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (247.89,121.86) {$N$};
\end{scope}
\begin{scope}
\path[clip] (231.96, 41.62) rectangle (411.55,110.68);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] (231.96, 41.62) rectangle (411.55,110.68);
\definecolor{drawColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round] (231.96, 45.09) --
	(411.55, 45.09);

\path[draw=drawColor,line width= 0.3pt,line join=round] (231.96, 68.35) --
	(411.55, 68.35);

\path[draw=drawColor,line width= 0.3pt,line join=round] (231.96, 91.60) --
	(411.55, 91.60);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.96, 56.72) --
	(411.55, 56.72);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.96, 79.97) --
	(411.55, 79.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.96,103.23) --
	(411.55,103.23);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (405.36, 41.62) --
	(405.36,110.68);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor,fill opacity=0.50] (240.12, 64.16) --
	(247.89, 60.85) --
	(255.67, 59.78) --
	(263.44, 69.26) --
	(271.22, 59.63) --
	(278.99, 57.31) --
	(286.77, 56.13) --
	(294.54, 57.00) --
	(302.32, 57.15) --
	(310.09, 59.83) --
	(317.87, 68.12) --
	(325.64, 69.02) --
	(333.41, 67.60) --
	(341.19, 71.94) --
	(348.96, 75.31) --
	(356.74, 78.25) --
	(364.51, 84.54) --
	(372.29, 85.40) --
	(380.06, 88.92) --
	(387.84, 93.02) --
	(395.61, 96.74) --
	(403.39,100.73) --
	(403.39,100.39) --
	(395.61, 96.28) --
	(387.84, 92.69) --
	(380.06, 88.71) --
	(372.29, 85.21) --
	(364.51, 81.29) --
	(356.74, 77.87) --
	(348.96, 74.21) --
	(341.19, 71.44) --
	(333.41, 67.10) --
	(325.64, 63.68) --
	(317.87, 61.35) --
	(310.09, 58.41) --
	(302.32, 56.50) --
	(294.54, 55.57) --
	(286.77, 54.88) --
	(278.99, 56.47) --
	(271.22, 58.80) --
	(263.44, 58.90) --
	(255.67, 58.75) --
	(247.89, 58.63) --
	(240.12, 59.84) --
	cycle;
